
%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Manavendra Sen Resume},
    pdfpagemode=FullScreen,
    }

\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage[most]{tcolorbox}



% Set the margins
\geometry{left=0.85cm, top=0.8cm, right=0.85cm, bottom=0.2cm}


% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]


%-------------------------
% Custom commands

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \hspace{-3mm}{#1}:\hspace{1mm} & \hspace*{0pt}\hfill{\footnotesize{ #3}} \vspace{-0.5mm}\\ \hspace{-2.9mm}#2 
    \end{tabular*}
    \vspace{0mm}
}

\newcommand{\resumeExp}[4]{
\vspace{0mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \hspace{-4.4mm} \small\textbf{#1} & {\footnotesize{#3}}\vspace{-1.2mm}\\
        \hspace{-4.3mm} \footnotesize{\text{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-6.1mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \hspace{-4.4mm} \small\textbf{#1} & {\footnotesize{#3}}\vspace{-1mm}\\
        \hspace{-4.3mm} \footnotesize{\text{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-6.5mm}
}

\newcommand{\resumeEdu}[4]{
\vspace{0mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \hspace{-4.3mm} \small\textbf{#1} & \footnotesize{#3}\vspace{-1mm} \\
        \hspace{-4.3mm} \footnotesize{#2} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-3.2mm}
}

\newcommand{\resumeAchieve}[3]
{
\hspace{-3.1mm}\textbf{ #1} & {#2} & \hspace{3mm}\footnotesize{#3}
\vspace{0mm}\\
}


\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm,itemsep=-2.5mm]}

\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-1.5mm}}

\renewcommand{\arraystretch}{1}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------



%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%

\newcommand{\name}{Manavendra Sen} % Your Name
\newcommand{\course}{B.Tech - Information Technology} % Your Course
% \newcommand{\roll}{199302058} % Your Roll No.
\newcommand{\phone}{7879071212} % Your Phone Number
\newcommand{\emaila}{manavendra4288@gmail.com} %Email 1
\newcommand{\github}{manavendrasen} %Github
\newcommand{\website}{https://manavendrasen.com/} %Website
\newcommand{\linkedin}{manavendrasen} %linkedin



\begin{document}
\fontfamily{cmr}\selectfont


%----------HEADING-----------------
\begin{center}
    \LARGE{\textbf{\name}}
\end{center}
\vspace{-6.5mm}
\begin{center}
    \small{\href{https://github.com/\github}{\faGithub \hspace{0.2mm} github.com/manavendrasen} |  \href{https://www.linkedin.com/in/\linkedin/}{\faLinkedinSquare \hspace{0.2mm} linkedin.com/in/manavendrasen} | \href{mailto:\emaila}{\faSend \hspace{0.2mm} \emaila} | \faPhone \hspace{0.2mm} \href{tel:\phone}{+91-\phone}}
\end{center}
\vspace{-3mm}

%-----------EDUCATION-----------------

\vspace{-2.5mm}
\section{Education}

\resumeSubHeadingListStart
\resumeEdu
{Manipal University Jaipur, Jaipur, India} 
{Bachelors of Technology in Information Technology} 
{Jul 2019 - Jun 2023} %Event Dates
{GPA: 9.48/10.0} %Website
\resumeSubHeadingListEnd
\vspace{-3.5mm}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeExp
{Dell Technologies}
{Undergraduate Intern - DevOps, GITLAB CICD, Salesforce}
{Jun 2022 - Aug 2022}
{Hyderabad, India}
\resumeItemListStart
\item[$\bullet$] Identifing immediate areas of improvement to increase DevOps Efficiency through
analysis.
\item[$\bullet$] Implementing scheduled builds and automated code migration from one salesforce environment
to another.
\item[$\bullet$] Integrating MS Teams/Email notifications for CICD pipeline events and deployment status.

\resumeItemListEnd

\resumeExp
{416 Marketing Inc}
{Software Development Engineer Intern - {MERN, PostgreSQL}}
{Jan 2022 - Mar 2022}
{Toronto, ON, Canada}
\resumeItemListStart
\item[$\bullet$] Compiled client requirement documentation and devised 2 production full-stack web applications within tight deadlines.
\item[$\bullet$] Conceptualized and streamlined the UI/UX frontend of 30+ app screens, by applying skills in colour theory and composition.
\resumeItemListEnd


\resumeExp
{Listnr, Inc}
{Software Development Engineer Intern - {React, Node.js, Express.js, MongoDB}}
{Jul 2021 - Sept 2021}
{Middletown, DE, USA}
\resumeItemListStart
\item[$\bullet$] Achieved 200+, 5-star reviews on AppSumo by implementing allows users to import podcasts from services like Spotify to Listnr and automatically generate customisable landing and promotional pages.
\item[$\bullet$] Delivered performance-driven and user experience-centric solutions which improved user retention by 75\%.
\item[$\bullet$] Collaborated effectively with the team to set up Sentry, which helped identify and troubleshoot bugs 60\% faster.
\resumeItemListEnd

\resumeExp
{Design In Situ}
{Full Stack Developer Intern - {React, Firebase}}
{Jun 2021 - Aug 2021}
{İstanbul, Turkey}
\resumeItemListStart
\item[$\bullet$] Planned and developed of music generation applications using ReactJS, Javascript, Tone.js, and Firebase with 500+ live users.
\item[$\bullet$] Coordinated with international clients to architect, develop and deploy 20+ microsites that met all business requirements.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5.5mm}

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeProject
{POPTALK!}
{React, Typescript, ExpressJS, NodeJS, Material UI, React Leaflet} %Project Name, Location Name
{Jul 2020 - Nov 2020} %Event Dates
{\href{https://devfolio.co/projects/poptalk-d6be}{Project},  \href{https://github.com/manavendrasen/poptalk}{Github}, \href{https://youtu.be/A6l8yGgv7YY}{Demo Video}} 
\resumeItemListStart
\item[$\bullet$] Implemented  a full-stack website and a chrome extension in 36 hours, which helps people discover new places to visit, connect and chat with people around the location, to resolve queries about the place.
\item[$\bullet$] Won the 1st prize at Hackstack’22, a National-Level Hackathon by IIIT Gwalior and Headout.
\resumeItemListEnd


\resumeProject
{MUJ HUB - One Stop Solution for everything in Manipal!} %Project Name
{React, React Native, Firebase, PostgreSQL, Express, Redux} %Project Name, Location Name
{Dec 2020 - Sept 2020} %Event Dates
{\href{https://play.google.com/store/apps/details?id=com.mujhub}{Play Store},  \href{https://www.mujhub.com/}{Website}}
\resumeItemListStart
\item[$\bullet$] Designed and developed the website and android app, used by more than 5000+ students daily, to get information about the hostel mess menu, order food online and manage their college attendance.
\item[$\bullet$] Generated 20,000+ as additional revenue for the food outlets by lifting sales by more than 200\%.
\resumeItemListEnd

\resumeProject
{Other Projects}{}{}{}
\vspace{-3mm}
\resumeItemListStart
\item[$\bullet$] \textbf{Clyde Chrome Extension \raisebox{-0.3mm}{\href{https://devpost.com/software/clyde-chrome-extension}{\footnotesize\faExternalLink}} :} Clyde is a chrome extension that uses multiple NLP techniques to analyze sentiments, behavioral traits and emotional traits for Youtube videos, news articles, tweets, or even subreddits in real-time \& get meaningful insights. 
\item[$\bullet$] \textbf{ACM Jaipur Professional Chapter Website \raisebox{-0.3mm}{\href{https://jaipur.acm.org/}{\footnotesize\faExternalLink}} :} Built and managed the Official website of ACM Jaipur Professional Chapter.
\resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-5.5mm}

\section{Achievements}
\vspace{0.2mm}
\resumeItemListStart
        \item[$\bullet$]\textbf{Honourable Mentions prize at "Build The World with Dolby.io" Hackathon 2021} \\ Project Link: \href{https://devpost.com/software/kit-h54t9m}{Kit - Improve your communication skills using Artificial Intelligence}
        \item[$\bullet$] \textbf{Silver medal winner at "The Freshworks Refresh App Challenge"  2021}\\ Project Link:  \href{https://devpost.com/software/wira}{Wira - AI-powered link repository for Freshservice}
\resumeItemListEnd

\vspace{-2.5mm}


\section{Technical Skills}
\vspace{0.2mm}

\small{\begin{tabular*}{\textwidth}[t]{p{0.5\textwidth} p{0.5\textwidth}}

\hspace{-3.1mm}{\textbf{ Programming languages:} C++, C, Java} & {\textbf{Web Technologies:} Javascript, Typescript, HTML5, CSS3} \\  
\hspace{-3.1mm}{\textbf{ Frameworks/Libraries:} React, Node.js, Express.js, React Native
} & {\textbf{Miscellaneous:} Git, Linux, Figma, PostgreSQL, MongoDB}
\end{tabular*}}

\vspace{-2.5mm}
\section{Volunteering}
\vspace{0.2mm}


% \small{\begin{tabular*}{\textwidth}[t]{p{\textwidth}}
% \hspace{-3.1mm}\textbf{ Computer Science: }{Data Structures and Algorithms, RDBMS, Operating Systems. Object }\\
% \hspace{-3.1mm}\textbf{ Mathematics: }{Optimization, Discrete Maths, Probability and Random Processes, Number Theory, Linear Algebra}
% \end{tabular*}}

% \vspace{-2.5mm}
% \section{Positions of Responsibility}
% \vspace{-0.4mm}



\resumeSubHeadingListStart
\resumePOR{\textbf{Technical Head, IEEE Computer Society MUJ}} % Position
{Facilitated mentorship sessions in various domains for 400+ mentees and 12 mentors.\\Mentored 200+ students on Git, and Github by organizing live workshops.}{\raisebox{0.75pt}{2021 - 2022}}
\resumeSubHeadingListEnd
\vspace{0mm}

%-------------------------------------------
\end{document}

