%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
    {\href{https://www.jpmorganchase.com/}{JPMorganChase}}{Feb 2025 -- Present}
    {Software Engineer II}{Bengaluru, Karnataka}
    \resumeItemListStart
        \resumeItem{Promoted to SDE II (top 10\%) and recognized with JPMC Impact Award 2024 for driving client-focused engineering improvements.}
        \resumeItem{Architected resilient \textbf{Java Spring Boot} microservices, achieving \textbf{~99.99\% uptime} with  multi-AZ Kubernetes deployment, ensuring zero major outages.}
        \resumeItem{Implemented critical workflow controls (Maker-Checker, Blind Rekey Validation) safeguarding high-value transactions ($>$\$10M+), reducing risk exposure and improving operational resilience.}    
        \resumeItem{Prototyped scalable solutions with \textbf{Google AI Agent Kit, LLMs, Drools, State Machine, AWS S3, and MSK} to support platform modernization.}
        % \resumeItem{Provided end-to-end ownership of production-grade full-stack cloud applications—conducting root cause analysis (RCA), implementing bug fixes, and executing maintenance activities to ensure stability and uptime.}
        \resumeItem{Mentored 5+ engineers, leading sessions on development and AI best practices.}
    \resumeItemListEnd

    \resumeSubheading
    {\href{https://www.jpmorganchase.com/}{JPMorganChase}}{Feb 2023  -- Jan 2025}
    {Software Engineer I}{Bengaluru, Karnataka}
    \resumeItemListStart
        \resumeItem{Rebuilt legacy FX system using \textbf{ReactJS UI, Java Spring Boot API, JUnit (Testing), and RDBMS/SQL (IBM DB2)}, enhancing scalability and maintainability.}
        \resumeItem{Designed and deployed fault-tolerant cloud architecture, leveraging \textbf{Docker} and \textbf{Kubernetes}. Achieved cross-region failover and disaster recovery. Implemented logging and monitoring using \textbf{Prometheus}, \textbf{Grafana}, logging sidecar pattern with \textbf{Fluentd}, and the \textbf{ELK}.}
        \resumeItem{Automated workflows, \textbf{saving 10+ hours per week} across teams by creating internal automation tools, libraries and code generation utilities using \textbf{Python, Golang}}
        \resumeItem{Improved data retrieval performance for high-volume queries (30K+ rows) by over 99\%, cutting response time from 5+ mins to $<$1 second, by implementing server-side caching using \textbf{Caffeine} and efficient key-based pagination, and gzip in transit.}
        % \resumeItem{Led design and engagement efforts for a 4,000+ member engineering community, handling internal communications, knowledge sharing, and cross-team collaboration initiatives.}
        \resumeItem{Created \textbf{React Native, Python FastAPI} app with \textbf{Razorpay} integration for an NGO as part of the Tech for Social Good initiative, capturing the entire waste collection and selling workflow with support for Kannada Localization.}
        % \resumeItem{Collaborated with product and design teams to identify user pain points and create intuitive UI prototypes and user journeys using \textbf{Figma}, improving usability and adoption.}
    \resumeItemListEnd

    % \resumeSubheading
    % {\href{https://huddle01.com/}{Huddle01}}{Oct 2022 -- Jan 2023}
    % {DevOps Intern - SRE, DevOps, Prometheus, Grafana, Docker, Kubernetes}{Remote}
    % \resumeItemListStart
    %     \resumeItem{Dockerized core components to enhance scalability and deployment efficiency: Containerized React App, Mediasoup Server, WebSocket signaling server, Redis, and RabbitMQ for streamlined orchestration and management.}
    %     \resumeItem{Configured monitoring, logging, and tracing for an event-driven microservice stack.}
    %     \resumeItem{Implemented the CI/CD pipeline on GitHub Actions to automate testing and deployment processes.}
    % \resumeItemListEnd

    \resumeSubheading
    {\href{https://www.dell.com/en-in}{Dell Technologies}}{Jun 2022 -- Aug 2022}
    {Software Engineer Summer Intern - DevOps, CICD}{Hyderabad, Telangana}
    \resumeItemListStart
        \resumeItem{Implemented GitLab CI pipelines and built reusable Linux bash scripts to send MS Teams/Email notifications for CI/CD pipeline events and deployment status.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
